Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-07 Dissertation/Thesis/tex/results.tex
added figures to 3D full exploration

>>>>

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_space_NW.JPG}
        		\caption{Northwest View}
    	\end{subfigure}
	\hspace*{0.05\columnwidth}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_space_NE.JPG}
        		\caption{Northeast View}
    	\end{subfigure}
	\caption{3D Exploration Space}
	\medskip
	\small
	The experimental space for full 3D exploration consists of normal lab objects such as tables and chairs, as well as a mannequin sitting at a desk and his parked bicycle.
	\label{fig:Full3DExplorationEnvironment}
\end{figure}

\begin{figure}[!t]
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_0min.jpg}
        		\caption{$0$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_0p25min.jpg}
        		\caption{$15$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_0p5min.jpg}
        		\caption{$30$ sec}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_1p5min.jpg}
        		\caption{$1.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_2p5min.jpg}
        		\caption{$2.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_3p5min.jpg}
        		\caption{$3.5$ min}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_4p5min.jpg}
        		\caption{$4.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_vid_4p75min.jpg}
        		\caption{$4.75$ min (end)}
    	\end{subfigure}
}
	\caption{Full 3D Autonomous Exploration Experiment}
	\medskip
	\small
	The robot completes a full yaw rotation over $20$ seconds, then autonomously explores the space. At $4$ min (j), the robot flies over the mannequin to explore the southeast corner of the room.
	\label{fig:exp3DVid}
\end{figure}

\begin{figure}[!t]
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_0min.jpg}
        		\caption{$0$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_0p25min.jpg}
        		\caption{$15$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_0p5min.jpg}
        		\caption{$30$ sec}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_1p5min.jpg}
        		\caption{$1.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_2p5min.jpg}
        		\caption{$2.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_3p5min.jpg}
        		\caption{$3.5$ min}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_4p5min.jpg}
        		\caption{$4.5$ min}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{explore3D_4p75min.jpg}
        		\caption{$4.75$ min (end)}
    	\end{subfigure}
}
	\caption{3D Occupancy Grid Map During Full 3D Autonomous Exploration}
	\medskip
	\small
	The robot (large axes) is controlled to track the desired pose (small axes), which follows a collision-free trajectory using Dijkstra's search toward candidates (top $75\%$ shown with red arrows, with greater opacity for larger expected information gains).
	\label{fig:exp3DOccMap}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{H_explore3D_test1.pdf}
	\caption{Entropy Change During Full 3D Experiment}
	\medskip
	\small
	The map entropy $H$ consistently decreases during the full 3D exploration experiment. Toward the end of the experiment, most cells that can be captured by the Asus Xtion have been updated, slowing down the rate of entropy decrease.
	\label{fig:Explore3D_H}
\end{figure}

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{connected_costmap.png}
        		\caption{Connected Cost Map Cross-Section}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{disconnected_costmap.png}
        		\caption{Disconnected Cost Map Cross-Section}
    	\end{subfigure}
	\caption{2D Cross-Sections of 3D Cost Maps}
	\medskip
	\small
	Two examples of the 3D cost maps from Dijkstra's search show connected and disconnected regions at the exploration height, where more blue regions have small distance costs, red regions have larger distance costs, and pink regions are unreachable due to collision risk. In (a), the robot does not have to change altitude to reach any of the collision-free poses. However in (b), the robot can only reach collision-free poses in the disconnected section by changing altitude.
	\label{fig:Full3DExplorationCostmaps}
\end{figure}
